Adopting agile software development in the large organizations: A systematic literature review

### 2014-08-12 journal/content.tex
Fixing layout
Introduction

Software organizations are constantly challenged to function more efficiently.
In the fast evolving software marketplace  . Agile methods have
been developed to improve efficiency of software development, but are originally
designed for use in projects of limited size.

The benefits of agile are pursued by large organizations

Agile methods are more difficult to implement in large organizations \citep{Dyba2008}.

It is an interesting topic, but agile in large scale is still an evolving
research topic.

-- What can be learned from this?

--> Motivation for research
-- There are no systematic reviews for this
-- A collection of experience reports can be used for creating a theoretical
   base.

--> Why is large-scale software development different from smaller scale?

This literature review is targeted for both practitioners and researchers. For
practitioners this work provides a reference of cases describing introduction
of agile methods, which can be valuable in planning or reflecting on a agile
adoption process. The systematic review approach can provide practitioners an
objective view on how agile adoptions typically progress.

Applying agile in large scale has been noted as a current research trend. In
2010 \citet{Freudenberg2010} conducted a survey at the XP conference,
highlighting ``agile and large projects'' as the one of the hottest research
topics. The trend was continued in the 2013 XP conference, where a research
trends workshop focused specifically on large scale agile development. The
viewpoint on introduction of agile methods was highlighted in the workshop
\citep{Dingsoyr2013a}.

@@

\begin{table}[t]
    \centering
    \begin{tabular}{ >{\raggedright\arraybackslash}p{0.31\textwidth}
                     >{\raggedright\arraybackslash}p{0.61\textwidth} }
        \toprule
        Code family          &  Description
        \\
        \midrule

>>>>

Software organizations are constantly challenged to function more efficiently.
In the fast evolving software marketplace companies must seek new ways to
respond to the competition. Agile methods have proven to improve efficiency and
quality \citep{Livermore2008}, which makes them attractive options when
considering ways for improving the development process. Agile methods give
advantage by enabling shorter lead times and stronger focus on customer needs
\citep{Petersen2010}.

However, agile methods have originally been designed for use in projects of
limited size \citep{Boehm2005}. It has proven that it may be problematic
to introduce agile practices in large organizations \citep{Dyba2009}.
Nevertheless, the benefits of agile are pursued by large organizations.
% It would also be sociatelly desirable to effectivize large software projects,
% because large projects often have societal influence.

% --> Why is large-scale software development different from smaller scale?
% Agile methods are more difficult to implement in large organizations
% \citep{Dyba2008}.
Compared to small organizations ideal for agile development, large organizations
are characterized by the need of additional coordination. A particular problem
in applying agile to large software organizations is how to handle inter-team
coordination. Large organizations also tend to have additional organizational
units that development must interface with, such as human resources.
Still further, large organizations may cause users and other stakeholders become
distant from development teams.
% The full set of requirements of a large system could be too cumbersome for
% individual teams to manage.
\citet{Boehm2003b} have suggested that sizable organizations should not attempt
to become fully agile.

This thesis presents a study on how large software organizations transform their
way of working towards agile methods. The focus of this study is to explain the
process of transformation, but we have decided to leave out discussion on
measuring the success of the transformation. The study has been performed as a
systematic literature review, drawing the conclusions from previously published
research. Using the systematic literature review method we aim to provide an
objective and broad view on the topic.

This study is targeted for both practitioners and researchers. For practitioners
this we provide a reference of cases describing introduction of agile methods,
which can be valuable in planning or reflecting on a agile adoption process. The
systematic literature review approach can provide practitioners an objective
view on how agile adoptions typically progress.

Applying agile in large scale has been noted as a current research trend. 
\citep{Freudenberg2010} conducted a survey at the 2010 XP conference,
highlighting ``agile and large projects'' as the one of the hottest research
topics. The trend was continued in the 2013 XP conference, where a research
trends workshop focused specifically on large scale agile development. The
viewpoint on introduction of agile methods was highlighted in the workshop
\citep{Dingsoyr2013a}.

@@

\begin{table}
    \centering
    \begin{tabular}{ >{\raggedright\arraybackslash}p{0.31\textwidth}
                     >{\raggedright\arraybackslash}p{0.61\textwidth} }
        \toprule
        Code family          &  Description
        \\
        \midrule
